Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-06 paper/main.tex
filling in analysis descriptions...

\paragraph*{Computing clustering scores and memory fingerprints.}

@@

\subsection*{Analysis}

\subsubsection*{Probability of first recall and probability of $n$\textsuperscript{th} recall}

\subsubsection*{Lag conditional response probability}

\paragraph{Temporal clustering score.}

@@

\subsubsection*{Serial position curves and recall accuracy}

>>>>

\paragraph*{Clustering scores and memory fingerprints.}

@@

\subsection*{Analyses}

\subsubsection*{Probability of $n$\textsuperscript{th} recall curves}

Probability of first recall curves~\citep{AtkiShif68, PostPhil65, WelcBurn24}
reflect the probability that an item will be recalled first, as a function of
its serial position during encoding. To carry out this analysis, we initialized (for each participant)
a number-of-lists (16) by number-of-words-per-list (16) matrix of zeros.
Then, for each list, we found the index of the word that was recalled first, and we filled in that
position in the matrix with a 1.  Finally, we averaged over the rows of the matrix to obtain a 1 by 16 array of
probabilities, for each participant.  We used an analogous procedure to compute probabilility of $n$\textsuperscript{th}
reacall curves for each participant.  Specifically, we filled in the corresponding matrices according to the $n$\textsuperscript{th}
recall on each list that each participant made.  When a given participant had made fewer than $n$ recalls for a given list,
we simply excluded that list from our analysis when computing that paritcipant's curve(s).

\subsubsection*{Lag-conditional response probability curve}

\paragraph*{Temporal clustering score.}

\subsubsection{Serial position curve}

@@
